\documentclass{article}
\usepackage{amssymb}

\title{
Computer Science G11 at The Dragon \\
Assignment 1 \\
Propositional Logic\\
\bf{Due date: Tue Sep. 18 2018}
}

\begin{document}
\maketitle
\date{Fri Sep. 2018}


\begin{enumerate}
\item (KtiCa) Express the following statements in propositional logic
\begin{enumerate}
\item I'm tired and hungry
\item If I'm hungry, I whinge
\item I only get tired if I did not have a nap
\item Either I eat dinner or I get hungry
\end{enumerate}
\item (Ktica) What does it mean that two logical expressions A and B are equivalent? Give an example.
\item \label{eqByTT} (KtiCa) Use the truth tables to decide which of the following pairs of propositions are equivalent. Hint: Just make one big truth table in
which you can discuss all cases.
\begin{enumerate}
\item $(p\,\vee\,q)\,\vee\,r $ and $p\,\vee\,(q\,\vee\,r)$
\item $(p\rightarrow q)\rightarrow r$ and $p\rightarrow (q\rightarrow r)$
\item $\urcorner (p\,\wedge\,q)$ and $\urcorner p\,\vee\,\urcorner q$
\item $p\rightarrow q$ and $\urcorner q \rightarrow \urcorner p$
\end{enumerate}
\item (kTIca) Repeat question \ref{eqByTT} this time using an algebraic method instead of truth tables.
\item (kTIca) A box has 3 buttons and a light. The light goes on when, and only when, exactly 2 buttons are pressed. Produce a truth table for 
such an setting. Using the truth table, find a formula (a proposition) for each case. Can you find a unique formula for the whole box?
\item (KticA) Simplify the boolean expression $\left[ (p\,\vee\,q\,\vee r)\,\wedge\,\urcorner (s\,\vee\,t)\right]\,\vee\,\left[ (p\,\vee\,q\,\vee r)\,\wedge\,(s\,\vee\,t)\right]$ 
and choose the best answer:
\begin{enumerate}
\item $p\,\vee\,q\,\vee\,r$
\item $s\,\vee\,t$
\item $\urcorner q\,\wedge\,\urcorner q\,\wedge\,\urcorner r$
\item $\urcorner s\,\wedge\, \urcorner t$
\item None of the above. Write your answer then.
\end{enumerate}
\item (KticA) Simplify the boolean expression $\left[\urcorner (p\,\vee\,q)\,\wedge\,\urcorner (r\,\vee\,s\,\vee\,t)\right]\,\vee\,\urcorner (q\,\vee\,q)$
and choose the best answer:
\begin{enumerate}
\item $p\,\vee\,q$
\item $\urcorner p\,\wedge\,\urcorner q$
\item $r\,\vee\,s\,\vee\,t$
\item $\urcorner r\,\wedge\,\urcorner s\,\wedge\, \urcorner t$
\item None of the above. Write your answer then.
\end{enumerate}
\item (KticA) Given the function $F(p,q,r)\,=\,\left[ p\,\wedge\,r\right]\,\vee\,\left[r\,\wedge\,(\urcorner p\,\vee\,(p\,\wedge\,q))\right]$ find the equivalent simplified 
expression for $F$
\begin{enumerate}
\item $r\,\vee\,(q\,\wedge\,r)$
\item $r\,\vee\,(p\,\wedge\,q\,\wedge\,r)$
\item $p\,\wedge\,r$
\item $p\,\vee\,(q\,\wedge\,r)$
\item $r$
\item None of the above. Write your answer then.
\end{enumerate}
\item (kTIca) Demonstrate algebraically that $(\urcorner p\rightarrow q)\,\wedge\,(p \rightarrow \urcorner q)$ is equivalent to 
$(\urcorner p\,\wedge\, r\,\wedge\, q)\,\vee\,(\urcorner r\,\wedge\, q\,\wedge\,\urcorner p)\,\vee\,(r\,\wedge\, p\,\wedge\, \urcorner q)\,\vee\,(\urcorner r\,\wedge\, p\,\wedge\,\urcorner q)$.
\item (kTIca) Argue algebraically wether $\urcorner p \rightarrow (q\,\vee\,r)$ is equivalent to $\urcorner ((p\rightarrow q)\,\vee\,r)$
\end{enumerate}
\end{document}
